---
title: Template for homework assignment reports
date: "Last compiled on: `r format(Sys.time(), '%d/%m/%Y, %H:%M:%S')`."
authors:
  - name: Paco de Lucía
    address: 778899
  - name: Baby Yoda
    address: 774455
  - name: Chick Corea
    address: 884422
  - name: An alternative for big teams, all in one line - Chick Corea (884422), Baby Yoda (774455), Paco de Lucía (778899), Suzanne Ciani (365411), and others. 
#  - name: Derek Zoolander
#    email: derek@example.com
#    address: Some Institute of Technology
abstract: |
  Summary of main findings and conclusions.
#acknowledgements: |
#  This is an acknowledgement.

keywords:
  - quantitative finance
  - financial risk
  - financial modeling in R
fontsize: 12pt
spacing: halfline # could also be oneline
#classoptions:
#  - endnotes
bibliography: mybibfile.bib
output: rticles::oup_article
#header-includes:
#  - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
#  - \usepackage{lineno} # For line numbering
#  - \linenumbers # For line numbering
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # By default, show code; set to FALSE to hide it
knitr::opts_chunk$set(fig.pos = 'H') # Places figures on pages separate from text
knitr::opts_chunk$set(out.width = '100%', dpi=300) # Figure resolution and size
knitr::opts_chunk$set(fig.env = "figure") # Latex figure environment
```

# Introduction.

*Look how you can add web links in the following sentence*. This template is based on the generic OUP template available [here](https://academic.oup.com/icesjms/pages/General_Instructions). *Now, look how you can add a different font, this is useful for file or function names* The original OUP sample tex document, providing more details on preferred formatting for LaTeX documents, is included with the template in the file `ouparticle_sample.tex`.

Here are some sample references. *Reference in brackets as in a list* Please see [@Hull; @carhart1997persistence] for a full discussion of multi-factor models. Bibliography will appear at the end of the document. *Second, without brackets, separated by a comma* See @Hull, @cochrane2009asset for a formal demonstration of analytical results, and [@carhart1997persistence; @cochrane1996cross] for some empirical results.

# Methodology.

An equation with a label for cross-referencing:

```{=tex}
\begin{equation}\label{eq:eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]
\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0
(\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}
```
This equation can be referenced as follows: Eq. \ref{eq:eq1}. Now a simpler equation:

```{=tex}
\begin{equation}\label{eq:eq2}
w=\sum^{20}_{i=1}[1/n^i]
\end{equation}
```

This equation can be referenced as Eq. \ref{eq:eq2}.

We can also write equations within the main text as here: $w=\sum^{20}_{i=1}[1/n^i]$.

## A subsection.

A numbered list:

1)  First numbered point

2)  Second numbered point

    -   Subpoint

A bullet list:

-   First point
-   Second point

# Results.

## Generate a figure.

```{r fig1, fig.cap = "This is the first figure.", echo = TRUE}
plot(1:10, main = "Some data", xlab = "Distance (cm)", ylab = "Time (hours)")
```

You can reference this figure as follows: Fig. \ref{fig:fig1}.

```{r fig2, fig.cap="This is the second figure.",echo=TRUE}
plot(1:5, pch = 19, main = "Some data", xlab = "Distance (cm)", ylab = "Time (hours)")
```

Reference to second figure: Fig. \ref{fig:fig2}

## Generate a table using `xtable`

```{r tab1, results="asis", echo=TRUE}
df = data.frame(ID = 1:3, code = letters[1:3])

# Creates tables that follow OUP guidelines using xtable
library(xtable) 
print(xtable(df, caption = "This is the table caption", label = "tab:tab1"),
      comment = FALSE)
```

You can reference this table as follows: Table \ref{tab:tab1}.

## Generate a table using `kable`.

```{r anothertable, echo=TRUE}
df = data.frame(ID = 1:3, code = letters[1:3])

# kable can alse be used for creating tables
knitr::kable(df, caption = "This is the table caption", format = "latex",
             booktabs = TRUE, label = "tab2")
```

You can reference this table as follows: Table \ref{tab:tab2}.

# Discussion.

You can cross-reference sections and subsections as follows: Section \ref{methodology.} and Section \ref{a-subsection.}.

***Note:*** the last section in the document will be used as the section title for the bibliography.

# References.
